When to Compete and When to Cooperate: Analysis on Strategies of Services within Communities

### 2012-12-13 papers/coopv3/IJWGS.tex
Added new paper

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{cite}
%\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}

%\newtheorem{property}{\textbf{Property}}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{When to Compete and When to Cooperate: Analysis on Strategies of Services within Communities}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%

\author{Babak Khosravifar$^1$\and Ehsan Khosrowshahi Asl$^2$
\and Jamal Bentahar$^2$\and Rabeb Mizouni$^3$\and Hadi Otrok$^3$}

%

% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published

\institute{$^1$McGill University, Canada, $^2$ Concordia University, Canada, $^3$Khalifa University, UAE\\
$babak.khosravifar@mcgill.ca$, $e\_khosr@encs.concordia.ca$, $bentahar@ciise.concordia.ca$,
$rabeb.mizouni@kustar.ac.ae$,$hadi.otrak@kustar.ac.ae$}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science} \tocauthor{Authors'
Instructions} \maketitle

\begin{abstract}
%Web services are business applications having the capability to
%cooperate within groups to increase the efficiency of serving
%customers.
Recently, a number of frameworks have been proposed to
aggregate web services within communities for the purpose of
enhancing their capabilities with respect to providing the
required services. Most of the proposed frameworks suggest that
web services within these communities are competing but also
exhibit cooperative behavior, so web services are said to be
coopetitive. However, deciding which strategy to adopt, which
means competing or cooperating is still an open question. The
purpose of this paper is to answer this question by discussing a
mechanism web services can use to effectively choose interacting
strategies which bring maximum utility. In this direction, we
investigate web services' characteristics and their expected
utilities over different strategies. We enable web services that
are hosted in communities with reasoning capabilities to enhance
their quality of  strategic interacting mechanisms as decision
making procedures. The ultimate objective is to measure the
threshold that web services can use in order to decide about
different interacting strategies. Moreover, we develop a simulated
environment where we analyze different scenarios and verify the
obtained theoretical results using parameters from a real web
services dataset. \keywords{Web services; Reputation; Strategies.}
\end{abstract}

@@

To analyze the expected payoffs obtained from different
strategies, web services need to compute the estimated
probabilities that distinguish subcases in each behaviorial status
($p_{w,CM}^t$ for competitive and $p_{w,CO}^t$ for cooperative).
To estimate these probabilities, we should notice that they are
functions of web services' reputation values ($Rep_w^t$).
Furthermore, $p_{w,CM}^t$ is also function of the difference
between the offered QoS ($QoS_w^t$) and the requested one
($T_{QoS}^t$); and $p_{w,CO}^t$ is function of the reputation of
other web services in the community because the leader is supposed
to be selective when it comes time to choose the collaborators. To
this end, we first discuss the desirable properties of an
estimation function of each of these probabilities, and show that
the proposed ones satisfy those properties. The desired properties
of $p_{w,CM}^t$ are as follows:

\begin{property}
$p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
and $T_{QoS}^t$.
\end{property}
%
\begin{property}
$p_{w,CM}^t$  is monotonically increasing/decreasing in $Rep^t_w$
and $QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
\end{property}
%
\begin{property}
$p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\begin{property}
The increase slope of $p_{w,CM}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\end{property}

@@

\noindent The desired properties of $p_{w,CO}^t$ are as follows:

\begin{property}
$p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
reputation of other web services in the community.
\end{property}
%
\begin{property}
$p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
 monotonically decreasing in the community average reputation.
\end{property}
%
%\begin{property}
%$p_{w,CM}$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
%\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\begin{property}
The increase slope of $p_{w,CO}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\end{property}

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.4]{graphcomp.eps}
\includegraphics[scale=0.4]{graphcoop.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}

@@

\begin{comment}

\section{Related Work}

In many frameworks proposed in the literature, service selection
and task allocation are regulated based on the reputation
parameter \cite{Jurca1,Jurca2}. In \cite{Ali}, the proposed
framework regulates the service selection based on the trust
policies expressed by the service users. In \cite{Maximilien2},
authors propose ontology for quality of service. Users compute the
web services' reputation using ratings. The frameworks proposed in
\cite{Kalepu,Maximilien1} address effective reputation mechanism
for web services. All these models address the reputation in
environments where web services function alone. In such models,
web service efficiency is not discussed in details and in general,
balancing the market share with the capacity is not considered as
an issue for web service besides his reputation.

There have been few work addressing the communities of web
service. The objective is to facilitate and improve the process of
web service selection and effectively regulate he process of
request and task allocation \cite{Jacyno}. In \cite{Khosravifar2},
authors propose a reputation-based architecture for communities
and investigate the collusion scenarios that might falsely
increase communities' reputation in the network. In
\cite{Khosravifar1}, the authors mainly address the overall
assessed reputation that is used as a main reason for service
selection. The authors do not consider truth/lie telling analysis
as a factor that impacts service selection in future.

The contribution of this paper is the proposition of a coopetitive
strategic model to analyze the interacting behavior of intelligent
web services that are active in communities of web services. The
proposed framework provides a reasoning technique that web
services can use to increase their overall obtained utilities. The
result of our proposed model is a probability distribution where
an intelligent web service can use over different interacting
strategies.

Our model has the advantage of being simple and  straightforward
in the contribution and the provided results. We considered two
acting strategies where web services expect different sort of
payoffs:  (1) $Competitive$ strategy where the web services claims
that it can accomplish a task and therefore, takes the
responsibility over the service consumer satisfaction; and (2)
$Cooperative$ strategy where the web service does not take the
responsibility to accomplish a task and only cooperates with other
$Competitive$ web services. As future work, we plan to emphasize
the service consumer role in the proposed model to obtain more
accurate results when consumer posts service satisfaction
feedback. Moreover, we would like to enhance  the reasoning
technique's features to cope with different unexpected scenarios.
We also need to expand the simulated environment to study
different scenarios in a number of perspectives.

\section{Conclusion}\label{Conclusion}
The contribution of this paper is the proposition of a
game-theoretic based model to analyze the best efficiency
characteristics for the active services in open networks. The
proposed framework considers the chances of web services in
joining a community in different cases with truthful and lying
information service agents. The proposed game analyzes the
existing Nash equilibrium and situations where the maximum payoff
is obtained.

Our model has the advantage of being simple and taking into
account three important factors: (1) rational services seek better
status in the environment by joining the community; (2) rational
information service agents obtain higher payoff by truth telling;
and (3) the community is obtaining more effective web services
while the information service agents challenge for providing
truthful information. As future work, we plan to consider the user
role in the game to obtain more accurate results when users act
rationally. Moreover, we would like to achieve a collusion
resistant efficiency mechanism, which is still an open problem in
open environments.

\end{comment}

@@

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[fleqn]{singlecol-new}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsfonts,amsmath,amscd, amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}

\usepackage{natbib}
%\usepackage[pdf]{graphicx}%
\def\newblock{\hskip .11em plus .33em minus .07em}

\makeatletter
\def\theequation{\arabic{equation}}

\makeatother

%\def\bmD{\mbox{\boldmath $D$}}        %99.10.1
%\def\bmE{\mbox{\boldmath $E$}}        %99.6.29
%\def\bmg{\mbox{\boldmath $g$}}
%\def\bmG{\mbox{\boldmath $G$}}
%\def\bmM{\mbox{\boldmath $M$}}
%\def\bmY{\mbox{\boldmath $Y$}}  %99.12.22
%\def\bmW{\mbox{\boldmath $W$}}  %99.12.22
%\def\bgamma{\mbox{\boldmath $\gamma$}}
%\def\tc#1{\textcolor{red}{\bf #1}}

\spaceskip=3.5pt plus1.47pt minus0.77pt \makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{page}{1}

\LRH{}
\RRH{}

\VOL{x}
\ISSUE{x}
\BottomCatch
\PAGES{xxxx}
\CLline
%\PUBYEAR{200x}

\subtitle{}

\title{When to Compete and When to Cooperate: Analysis on Strategies of Services within Communities}

\authorA{author}

\affA{Address}

\begin{abstract}
Recently, a number of frameworks have been proposed to
aggregate web services within communities for the purpose of
enhancing their capabilities with respect to providing the
required services. Most of the proposed frameworks suggest that
web services within these communities are competing but also
exhibit cooperative behavior, so web services are said to be
coopetitive. However, deciding which strategy to adopt, which
means competing or cooperating is still an open question. The
purpose of this paper is to answer this question by discussing a
mechanism web services can use to effectively choose interacting
strategies which bring maximum utility. In this direction, we
investigate web services' characteristics and their expected
utilities over different strategies. We enable web services that
are hosted in communities with reasoning capabilities to enhance
their quality of  strategic interacting mechanisms as decision
making procedures. The ultimate objective is to measure the
threshold that web services can use in order to decide about
different interacting strategies. Moreover, we develop a simulated
environment where we analyze different scenarios and verify the
obtained theoretical results using parameters from a real web
services dataset.
\end{abstract}

\KEYWORD{Web services; Reputation; Strategies.}

\REF{to this paper should be made as follows: Author. (xxxx) `Title', {\it Int. J. }, Vol.~x, No.~x, pp.xxx--xxx.}

\begin{bio}

\end{bio}

\maketitle

@@

To analyze the expected payoffs obtained from different
strategies, web services need to compute the estimated
probabilities that distinguish subcases in each behaviorial status
($p_{w,CM}^t$ for competitive and $p_{w,CO}^t$ for cooperative).
To estimate these probabilities, we should notice that they are
functions of web services' reputation values ($Rep_w^t$).
Furthermore, $p_{w,CM}^t$ is also function of the difference
between the offered QoS ($QoS_w^t$) and the requested one
($T_{QoS}^t$); and $p_{w,CO}^t$ is function of the reputation of
other web services in the community because the leader is supposed
to be selective when it comes time to choose the collaborators. To
this end, we first discuss the desirable properties of an
estimation function of each of these probabilities, and show that
the proposed ones satisfy those properties. The desired properties
of $p_{w,CM}^t$ are as follows:
\\

\noindent\textit{Property 1.}
$p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
and $T_{QoS}^t$.
\\

%
\noindent\textit{Property 2.}
$p_{w,CM}^t$  is monotonically increasing/decreasing in $Rep^t_w$
and $QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
\\

%
\noindent\textit{Property 3.}
$p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
\\

%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\noindent\textit{Property 4.}
The increase slope of $p_{w,CM}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\\

@@

\noindent The desired properties of $p_{w,CO}^t$ are as follows:
\\

\noindent\textit{Property 5.}
$p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
reputation of other web services in the community.
\\

%
\noindent\textit{Property 6.}
$p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
 monotonically decreasing in the community average reputation.
\\

%
%\begin{property}
%$p_{w,CM}$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
%\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%

\noindent\textit{Property 7.}
The increase slope of $p_{w,CO}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\\

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.4]{graphcomp.eps}
\includegraphics[scale=0.4]{graphcomp.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%START YOUR SAMPLE TEXT HERE%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
